---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BaZING

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/Goodrich-Lab/BaZING/branch/main/graph/badge.svg)](https://app.codecov.io/gh/Goodrich-Lab/BaZING?branch=main)
<!-- badges: end -->


## Contents

- [Overview](#overview)
- [Installation](#overview)
- [Example](#example)



## Overview

The goal of BaZING is to ...


## Installation

You can install the development version of BaZING from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Goodrich-Lab/BaZING")
```


## Example

The following example comes from the data in ... 


```{r example}
library(BaZING)

# Load example data
data("iHMP")

object <- Format_BaHZING(iHMP)
```






<!-- delete information below this line before final submission -->


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
# plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
