---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BaZING: Bayesian Hierarchical Zero-Inflated Negative Binomial Regression with G-Computation

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/Goodrich-Lab/BaZING/branch/main/graph/badge.svg)](https://app.codecov.io/gh/Goodrich-Lab/BaZING?branch=main)
<!-- badges: end -->


## Contents

- [Overview](#overview)
- [Installation](#overview)
- [Example](#example)



## Overview

This platform is dedicated to the analysis of environmental mixture exposures and other mixture exposures with hierarchical gut microbiome outcome data. BaZING, short for Bayesian Hierarchical Zero-Inflated Negative Binomial Regression with G-Computation, is a powerful toolkit designed to uncover intricate relationships between environmental exposures and gut microbiome outcomes.


## Installation

You can install the development version of BaZING from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Goodrich-Lab/BaZING")
```


## Example

The following example comes from the data in iHMP publically available dataset 


```{r example}
library(BaZING)

### Load example data
data("iHMP_Reduced")

### Format microbiome data
formatted_data <- Format_BaHZING(iHMP_Reduced)

### Perform Bayesian hierarchical zero-inflated negative binomial regression with g-computation
### Specify a mixture of exposures
x <- c("soft_drinks_dietnum","diet_soft_drinks_dietnum","fruit_juice_dietnum","water_dietnum",
       "alcohol_dietnum","yogurt_dietnum","dairy_dietnum","probiotic_dietnum","fruits_no_juice_dietnum",
       "vegetables_dietnum","beans_soy_dietnum","whole_grains_dietnum","starch_dietnum","eggs_dietnum",
       "processed_meat_dietnum","red_meat_dietnum","white_meat_dietnum","shellfish_dietnum","fish_dietnum",
       "sweets_dietnum")

### Specify a set of covariates
covar <- c("consent_age","sex",paste0("race",0:3),paste0("educ",0:7))

###Set exposure standaridization to standard_normal or quantiles
exposure_standardization = "standard_normal"

### Perform BaH-ZING 
results <- BaZING_Model(formatted_data,covar,x,exposure_standardization)
```






<!-- delete information below this line before final submission -->


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
# plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
